\documentclass[11pt]{article}

%\renewcommand\familydefault{\sfdefault}
 
%input preamble and macros
\input{preamble}
\input{macros}

 
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
\usepackage[linewidth=1pt]{mdframed}
\usepackage{proof}
%\newcommand{\N}{\mathbb{N}}
%\newcommand{\Z}{\mathbb{Z}}

% Named environments (no counters) 
\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
%\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
%\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
 
% Environments with counters
\newtheoremstyle{myplain} {5mm}% ⟨Space above⟩
{3mm}% ⟨Space below⟩
{}% ⟨Body font⟩
{}% ⟨Indent amount⟩
{\bfseries}% ⟨Theorem head font⟩
{.}% ⟨Punctuation after theorem head⟩
{.5em}% ⟨Space after theorem head⟩2
{}% ⟨Theorem head spec (can be left empty, meaning ‘normal’)⟩

\date{}

\theoremstyle{myplain}
\newtheorem{exercise}{Exercise}

\theoremstyle{definition} % no italics
\newtheorem{subexercise}{}[exercise]

\newcommand{\subex}[1]{\begin{subexercise}#1\end{subexercise}}

\begin{document}
 
% --------------------------------------------------------------
%                         Start here
% --------------------------------------------------------------
 
\title{Cyber-Physical Computation
\\ {\small First Assignment -- the case of an airfield}}
\author{Renato Neves}
 
\maketitle

Consider a private airfield used by 2 planes, which can be either flying,
parked, landing, or taking off. The landing field is a resource shared by the
two planes, and the following requirements must be met:
\begin{enumerate}
  \item only 1 plane can use the landing field at a time;
  \item a Controller component receives requests to \emph{land} or to \emph{take off}, and replies with a \emph{wait} signal when the field is unavailable;
  \item each plane sends requests to the Controller to \emph{land} or to \emph{take off}, and sends notifications when the field becomes \emph{free};
  \item the Controller has 5 time units to notify a plane to wait;
  \item after 5 time units from requesting access to the field and with no wait signal, the planes take another 5 time units to reach the field;
  \item each plane takes non-deterministically between 1-3 time units to take off, and between 4-6 time units to land and park;
  \item after taking off and after parking the planes notify the Controller with a \emph{gone} signal;
  \item if a plane is told to wait, we assume it will take between 5-7 time units to reach the field.
\end{enumerate}

\noindent
Suggest a \textsc{Uppaal} model for the planes and the controller. List 4 to 8
desired properties that the model should satisfy. Verify the properties via
\textsc{Uppaal}.

\smallskip
\noindent {\underline{Extra points}:} Extend your model to handle $n$ planes at
once. Can you think of other useful features that the airfield should have? If
so please discuss them and describe how would you model them.

\bigskip

\begin{mdframed}  
  \myparagraph{What to submit:} A single report in PDF for all tasks 
  \textbf{and} all the relevant source files. 
  Send by email
  (\underline{nevrenato@gmail.com}) a unique zip file
  ``\bash{cpc2425-N.zip}'', where \bash{N} is your
  student numbers. The subject of the email should be ``\bash{cpc2425
    N first assignment}''.

\myparagraph{Deadline:} 10th April 2025 @ 23h59
\end{mdframed}

\end{document}
